Adaptive Exponentiated Gradient

### 2014-01-27 lp/matrix.tex
proofread a first draft, now just need to add a conclusion

\section{Extension to Matrices} 
\label{sec:matrix}
We now extend our results to the matrix setting. Here $W$ is a positive semidefinite 
matrix. The analogue to the simplex is constrainint $\Tr(W)$ to be $1$. Instead of a vector 
of losses $z_t$, we have a matrix of losses $Z_t$, which is assumed to be symmetric and to 
have all eigenvalues between $-1$ and $1$. The loss in round $t$ is $\Tr(W_t^{\top}Z_t)$. 
Since all matrices involves are symmetric, we will typically suppress the transpose and 
just write $\Tr(W_tZ_t)$. Note that we can embed the vector setting in the matrix setting 
by restricting to diagonal matrices.

We start with an extension of Proposition~\ref{prop:aeg} to the matrix setting:
\begin{proposition}
\label{prop:maeg}
Consider the updates given by $\Theta_1 = -\log(n)I$ and 
$\Theta_{t+1} = \Theta_t - \eta Z_t - \eta^2 (Z_t - M_t)^2$, 
with prediction $W_t = \frac{\exp(\Theta_t - \eta M_t)}{\Tr(\exp(\Theta_t - \eta M_t))}$. For this algorithm,
\begin{equation}
\Regret(w) \leq \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n \Tr(W(Z_t-M_t)^2).
\end{equation}
\end{proposition}
\begin{proof}
When $\psi(W) = \Tr(W\log(W))$ and $S$ consists of positive semidefinite 
matrices with trace $1$, the prediction $W_t$ corresponds to 
$\nabla \psi_S^*(\Theta_t - \eta M_t)$. So, again, it suffices to check 
that the condition of Corolarry~\ref{cor:a-o2} is satisfies for 
$U_t = (Z_t - M_t)^2$. To do so, we need to make use of the 
Golden-Thompson inequality $\Tr(\exp(A+B)) \preceq \Tr(\exp(A)\exp(B))$, 
together with the fact that $-X-X^2 \preceq \log(I-X)$ for 
$-\frac{1}{2}I \preceq X \preceq \frac{1}{2}I$. We then have
\begin{align*}
\lefteqn{\psi^*(\Theta_t - \eta Z_t - \eta^2 U_t)} \\
 &= \Tr(\exp(\Theta_t - \eta Z_t - \eta^2 (Z_t - M_t)^2)) \\
 &\leq \Tr(\exp(\Theta_t - \eta M_t)\exp(-\eta (Z_t - M_t) - \eta^2 (Z_t - M_t)^2)) \\
 &\leq \Tr(\exp(\Theta_t - \eta M_t)(I - \eta (Z_t - M_t))) \\
 &= \Tr(\exp(\Theta_t - \eta M_t)) - \eta \Tr(\exp(\Theta_t - \eta M_t)(Z_t - M_t)) \\
 &= \psi^*(\Theta_t - \eta M_t) - \eta \langle \nabla \psi^*(\Theta_t - \eta M_t), Z_t - M_t \rangle.
\end{align*}
This verifies the condition of Corolarry~\ref{cor:a-o2}, so that we have 
a regret bound of $\frac{\psi_S^*(0) + \psi(W)}{\eta} + \eta \sum_{t=1}^T \Tr(WU_t)$. 
Finally, noting that $\psi_S^*(0) = \log(n)$, $\psi(W) = \Tr(W\log(W)) \leq 0$, and 
$U_t = (Z_t - M_t)^2$ completes the proof.
\end{proof}
We would now, as in Section~\ref{sec:ftrl-aux}, like to learn $M_t$ adaptively 
to be competitive with the best fixed value $M^*$. However, it isn't even clear 
that such a best fixed value exists (since the optimal value may depend on $W$). 
Lemma~\ref{lem:global-opt} addresses this issue (proved in slightly greater 
generality for later convenience):
\begin{lemma}
\label{lem:global-opt}
For any $\delta \geq 0$, define $M^* \eqdef \frac{1}{T+\delta} \sum_{t=1}^T Z_t$. Then, for 
any $M' \neq M^*$, we have
\begin{equation*} \delta (M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2 \preceq \delta (M')^2 + \sum_{t=1}^T (Z_t-M')^2. \end{equation*}
\end{lemma}
\begin{proof}
Write $M' = M^* + D$. Then we have
\begin{dgroup*}
\begin{dmath*} \delta(M')^2 + \sum_{t=1}^T (Z_t - M')^2
\end{dmath*}\begin{dmath*}  = \delta(M^*+D)^2 + \sum_{t=1}^T (Z_t - M^* - D)^2 
\end{dmath*}\begin{dmath*}  = \delta(M^*)^2 + \sum_{t=1}^T (Z_t - M^*)^2 + \left[\delta M^* + \sum_{t=1}^T M^*-Z_t\right]D + D\left[\delta M^* + \sum_{t=1}^T M^*-Z_t\right] + TD^2 
\end{dmath*}\begin{dmath*}  = \delta(M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2 + TD^2 
\end{dmath*}\begin{dmath*}  \succeq \delta(M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2,
\end{dmath*}
\end{dgroup*}
which completes the lemma.
\end{proof}
Setting $\delta$ to $0$, we now see that $\frac{1}{T} \sum_{t=1}^T Z_t$ is the 
optimal value of $M^*$ for any $W \succeq 0$, in analogy with the vector case. We 
remark that Lemma~\ref{lem:global-opt} is almost purely algebraic, and only relies 
on the property that $D^2 \succeq 0$ for any symmetric matrix $D$. We could obtain 
a similar lemma for any partially ordered algebra equipped with an adjoint operator 
$*$ such that $a^{*}a \succeq 0$ for all elements $a$ of the algebra.

Lemma~\ref{lem:global-opt} gives us a target value for the $M_t$, but we cannot 
simply apply the standard Follow the Regularized Leader lemma. This is because 
we need a result of the form
\[ \sum_{t=1}^T (Z_t - M_t)^2 \preceq \sum_{t=1}^T (Z_t - M^*) + \epsilon I, \]
which cannot be straightforwardly expressed as a regret bound. We deal with this 
by deriving a generalization of the FTRL algorithm, which we call FTRL-$\sK$. 
This is an algorithm in which losses are vector-valued and we obtain regret relative 
to a partial ordering defined by a cone $\sK$.

An important notion is that of a \emph{global optimum}. For a function $f : X \to \bR^n$ 
and a cone $\sK \subset \bR^n$, we say that $f$ has a global optimum relative to 
$\sK$ if there exists an $x$ such that $f(x) \leq_{\sK} f(y)$ for all $y \in X$.

\begin{lemma}
\label{lem:ftrl-k}
Suppose that for all $1 \leq t \leq T+1$, there 
exists a global minimizer $M_t$ of 
$\psi(M) + \sum_{s=1}^{t-1} f_s(M)$. Then for all $M$,
\begin{dmath} \sum_{t=1}^T f_t(M_t)-f_t(M) \leq_{\sK} \psi(M) - \psi(M_1) + \sum_{t=1}^T f_t(M_{t}) - f_t(M_{t+1}). \end{dmath}
\end{lemma}
\begin{proof}
We will prove the lemma by induction on $T$. Note that the lemma is equivalent to showing that 
\[ \psi(M_1) + \sum_{t=1}^T f_t(M_{t+1}) \leq_{\sK} \psi(M) + \sum_{t=1}^T f_t(M) \]
for all $M$.

In the base case $T = 0$, we have
\[ \psi(M_1) \leq_{\sK} \psi(M), \]
which follows from the fact that $M_1$ is a global minimizer of $\psi$ and 
hence $\psi(M_1) \leq_{\sK} \psi(M)$ for all $M$. For the inductive step, suppose that
\[ \sum_{t=1}^{T-1} f_t(M_{t+1}) \leq_{\sK} \psi(M) \sum_{t=1}^{T-1} f_t(M) \]
for all $M$, and invoke this for the particular choice $M = M_{T+1}$. Then we have
\begin{align*}
\lefteqn{\psi(M_1) + \sum_{t=1}^T f_t(M_{t+1})} \\
 &= \psi(M_1) + \sum_{t=1}^{T-1} f_t(M_{t+1}) + f_T(M_{T+1}) \\
 &\leq_{\sK} \psi(M_{T+1}) + \sum_{t=1}^{T-1} f_t(M_{T+1}) + f_T(M_{T+1}) \\
 &= \psi(M_{T+1}) + \sum_{t=1}^T f_t(M_{T+1}) \\
 &\leq_{\sK} \psi(M) + \sum_{t=1}^T f_t(M)
\end{align*}
for all $M$, where we use the fact that $M_{T+1}$ is a global minimizer of $\psi(M) + \sum_{t=1}^T f_t(M)$ for 
the last inequality. This completes the inductive hypothesis and hence the proof.
\end{proof}

As a corollary, we have (compare to Proposition~\ref{prop:ftrl-aux}):
\begin{corollary}
\label{cor:ftrl-k-aux}
Suppose that we choose $M_t = \frac{1}{t} \sum_{s=1}^{t-1} Z_s$. Then
\[ \sum_{t=1}^T (Z_t - M_t)^2 \preceq 2\sum_{t=1}^T (Z_t - M^*)^2 + 6I, \]
for $M^* \eqdef \frac{1}{T} \sum_{t=1}^T Z_t$.
\end{corollary}
\begin{proof}
The key observation is the \emph{matrix Young's inequality}: 
$AB + BA \preceq \frac{1}{\gamma}A^2 + \gamma B^2$ for all symmetric $A$, $B$ and 
all $\gamma > 0$. (This follows immediately upon expanding 
$(A/\sqrt{\gamma} - \sqrt{\gamma} B)^2 \succeq 0$.) We then note that 
$M_t$ obeys Lemma~\ref{lem:ftrl-k} with $\psi(M) = M^2$ and $f_t(M) = (M-Z_t)^2$. 
Hence we have
\begin{dgroup*}
\begin{dmath*} \sum_{t=1}^T (Z_t - M_t)^2 - (Z_t - M^*)^2
\end{dmath*}\begin{dmath*} = (M^*)^2 + \sum_{t=1}^T (Z_t - M_t)^2 - (Z_t - M_{t+1})^2 
\end{dmath*}\begin{dmath*} = (M^*)^2 + \sum_{t=1}^T Z_t(M_{t+1} - M_t) + (M_{t+1}-M_t)Z_t + M_t^2 - M_{t+1}^2 
\end{dmath*}\begin{dmath*} = (M^*)^2 + M_1^2 - M_{T+1}^2 + \sum_{t=1}^T \frac{1}{t+1}\left[ Z_t(Z_t-M_t) + (Z_t-M_t)Z_t\right] 
\end{dmath*}\begin{dmath*} \leq I + \sum_{t=1}^T \frac{Z_t^2}{\gamma (t+1)^2} + \gamma (Z_t - M_t)^2 
\end{dmath*}\begin{dmath*} \leq I + \frac{I}{\gamma} + \gamma \sum_{t=1}^T (Z_t - M_t)^2.
\end{dmath*}
\end{dgroup*}
Re-arranging yields
\begin{equation*}
\sum_{t=1}^T (Z_t - M_t)^2 \leq \frac{1}{1-\gamma} \left( \frac{1+\gamma}{\gamma}I + \sum_{t=1}^T (Z_t - M^*)^2\right),
\end{equation*}
which for $\gamma = \frac{1}{2}$ again yields the desired result.
\end{proof}
Combining Proposition~\ref{prop:maeg} with Corollary~\ref{cor:ftrl-k-aux} gives a 
regret bound for the MEG-Variance algorithm, whose updates are given in 
Table~\ref{tab:algorithms}.
\begin{corollary}
\label{cor:maeg-variance}
The MEG-Variance algorithm achieves a regret bound of
\begin{dmath}\Regret(w) \leq \frac{\log(n)}{\eta} + \eta \left[ \sum_{t=1}^T \Tr(W(Z_t-M^*)^2) + 4\log(T+1) \right].\end{dmath} 
\end{corollary}

>>>>

\section{Extension to Matrices} 
\label{sec:matrix}
We now extend our results to the matrix setting. Here $W$ is a positive semidefinite 
matrix. The analogue to the simplex is constraining $\Tr(W)$ to be $1$. Instead of a vector 
of losses $z_t$, we have a matrix of losses $Z_t$, which is assumed to be symmetric and to 
have all eigenvalues between $-1$ and $1$. The loss in round $t$ is $\Tr(W_t^{\top}Z_t)$. 
Since all matrices involved are symmetric, we will typically suppress the transpose and 
just write $\Tr(W_tZ_t)$. Note that we can embed the vector setting in the matrix setting 
by restricting to diagonal matrices.

We start with an extension of Proposition~\ref{prop:aeg} to the matrix setting:
\begin{proposition}
\label{prop:maeg}
Consider the updates given by $\Theta_1 = 0$ and 
$\Theta_{t+1} = \Theta_t - \eta Z_t - \eta^2 (Z_t - M_t)^2$, 
with prediction $W_t = \frac{\exp(\Theta_t - \eta M_t)}{\Tr(\exp(\Theta_t - \eta M_t))}$. For $0 < \eta \leq \frac{1}{4}$, $\|Z_t\|_{op} \leq 1$, and $\|M_t\|_{op} \leq 1$, we have
\begin{equation}
\Regret(w) \leq \frac{\log(n)}{\eta} + \eta \sum_{i=1}^n \Tr(W(Z_t-M_t)^2)
\end{equation}
for all $W \succeq 0$ with $\Tr(W) = 1$.
\end{proposition}
\begin{proof}
When $\psi(W) = \Tr(W\log(W))$ and $S$ consists of positive semidefinite 
matrices with trace $1$, the prediction $W_t$ corresponds to 
$\nabla \psi_S^*(\Theta_t - \eta M_t)$. So, again, it suffices to check 
that the condition of Corollary~\ref{cor:a-o2} is satisfies for 
$U_t = (Z_t - M_t)^2$. To do so, we need to make use of the 
Golden-Thompson inequality $\Tr(\exp(A+B)) \preceq \Tr(\exp(A)\exp(B))$ \cite{golden, thompson}, 
together with the fact that $-X-X^2 \preceq \log(I-X)$ for 
$-\frac{1}{2}I \preceq X \preceq \frac{1}{2}I$. We then have
\begin{align*}
\lefteqn{\psi^*(\Theta_t - \eta Z_t - \eta^2 U_t)} \\
 &= \Tr(\exp(\Theta_t - \eta Z_t - \eta^2 (Z_t - M_t)^2)) \\
 &\leq \Tr(\exp(\Theta_t - \eta M_t)\exp(-\eta (Z_t - M_t) - \eta^2 (Z_t - M_t)^2)) \\
 &\leq \Tr(\exp(\Theta_t - \eta M_t)(I - \eta (Z_t - M_t))) \\
 &= \Tr(\exp(\Theta_t - \eta M_t)) - \eta \Tr(\exp(\Theta_t - \eta M_t)(Z_t - M_t)) \\
 &= \psi^*(\Theta_t - \eta M_t) - \eta \langle \nabla \psi^*(\Theta_t - \eta M_t), Z_t - M_t \rangle.
\end{align*}
This verifies the condition of Corolarry~\ref{cor:a-o2}, so that we have 
a regret bound of $\frac{\psi_S^*(0) + \psi(W)}{\eta} + \eta \sum_{t=1}^T \Tr(WU_t)$. 
Finally, noting that $\psi_S^*(0) = \log(n)$, $\psi(W) = \Tr(W\log(W)) \leq 0$, and 
$U_t = (Z_t - M_t)^2$ completes the proof.
\end{proof}
We would now, as in Section~\ref{sec:ftrl-aux}, like to learn $M_t$ adaptively 
to be competitive with the best fixed value $M^*$. However, it is no longer clear 
that such a best fixed value exists (since the optimal value may depend on $W$). 
Lemma~\ref{lem:global-opt} addresses this issue (proved in slightly greater 
generality for later convenience):
\begin{lemma}
\label{lem:global-opt}
For any $\delta \geq 0$, define $M^* \eqdef \frac{1}{T+\delta} \sum_{t=1}^T Z_t$. Then, for any symmetric matrix $M'$, we have
\begin{equation*} \delta (M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2 \preceq \delta (M')^2 + \sum_{t=1}^T (Z_t-M')^2. \end{equation*}
\end{lemma}
\begin{proof}
Write $M' = M^* + D$. Then we have
\begin{dgroup*}
\begin{dmath*} \delta(M')^2 + \sum_{t=1}^T (Z_t - M')^2
\end{dmath*}\begin{dmath*}  = \delta(M^*+D)^2 + \sum_{t=1}^T (Z_t - M^* - D)^2 
\end{dmath*}\begin{dmath*}  = \delta(M^*)^2 + \sum_{t=1}^T (Z_t - M^*)^2 + \left[\delta M^* + \sum_{t=1}^T M^*-Z_t\right]D + D\left[\delta M^* + \sum_{t=1}^T M^*-Z_t\right] + TD^2 
\end{dmath*}\begin{dmath*}  = \delta(M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2 + TD^2 
\end{dmath*}\begin{dmath*}  \succeq \delta(M^*)^2 + \sum_{t=1}^T (Z_t-M^*)^2,
\end{dmath*}
\end{dgroup*}
which completes the lemma.
\end{proof}
Setting $\delta$ to $0$, we now see that $\frac{1}{T} \sum_{t=1}^T Z_t$ is the 
optimal value of $M^*$ for any $W \succeq 0$, in analogy with the vector case. We 
remark that Lemma~\ref{lem:global-opt} is almost purely algebraic, and only relies 
on the property that $D^2 \succeq 0$ for any symmetric matrix $D$. We could obtain 
a similar lemma for any partially ordered algebra equipped with an adjoint operator 
$*$ such that $a^{*}a \succeq 0$ for all elements $a$ of the algebra.

Lemma~\ref{lem:global-opt} gives us a target value for the $M_t$, but we cannot 
simply apply the standard Follow the Regularized Leader lemma. This is because 
we need a result of the form
\[ \sum_{t=1}^T (Z_t - M_t)^2 \preceq \sum_{t=1}^T (Z_t - M^*)^2 + \epsilon I, \]
which cannot be straightforwardly expressed as a regret bound. We deal with this 
by deriving a generalization of the FTRL algorithm, which we call FTRL-$\sK$. 
This is an algorithm in which losses are vector-valued and we obtain regret relative 
to a partial ordering defined by a cone $\sK$.

An important notion is that of a \emph{global minimizer}. For a function $f : X \to \bR^n$ 
and a cone $\sK \subset \bR^n$, we say that $x$ is a global minimizer of $f$ 
relative to $\sK$ if $f(x) \leq_{\sK} f(y)$ for all $y \in X$.

\begin{lemma}[FTRL-$\sK$]
\label{lem:ftrl-k}
Suppose that for all $1 \leq t \leq T+1$, there 
exists a global minimizer $M_t$ of 
$\psi(M) + \sum_{s=1}^{t-1} f_s(M)$. Then for all $M$,
\begin{dmath} \sum_{t=1}^T f_t(M_t)-f_t(M) \leq_{\sK} \psi(M) - \psi(M_1) + \sum_{t=1}^T f_t(M_{t}) - f_t(M_{t+1}). \end{dmath}
\end{lemma}
\begin{proof}
We will prove the lemma by induction on $T$. Note that the lemma is equivalent to showing that 
\[ \psi(M_1) + \sum_{t=1}^T f_t(M_{t+1}) \leq_{\sK} \psi(M) + \sum_{t=1}^T f_t(M) \]
for all $M$. In the base case $T = 0$, we have
\[ \psi(M_1) \leq_{\sK} \psi(M), \]
which follows from the fact that $M_1$ is a global minimizer of $\psi$ and 
hence $\psi(M_1) \leq_{\sK} \psi(M)$ for all $M$. For the inductive step, suppose that
\[ \sum_{t=1}^{T-1} f_t(M_{t+1}) \leq_{\sK} \psi(M) \sum_{t=1}^{T-1} f_t(M) \]
for all $M$, and invoke this for the particular choice $M = M_{T+1}$. Then we have
\begin{align*}
\lefteqn{\psi(M_1) + \sum_{t=1}^T f_t(M_{t+1})} \\
 &= \psi(M_1) + \left[\sum_{t=1}^{T-1} f_t(M_{t+1})\right] + f_T(M_{T+1}) \\
 &\leq_{\sK} \psi(M_{T+1}) + \left[\sum_{t=1}^{T-1} f_t(M_{T+1})\right] + f_T(M_{T+1}) \\
 &= \psi(M_{T+1}) + \sum_{t=1}^T f_t(M_{T+1}) \\
 &\leq_{\sK} \psi(M) + \sum_{t=1}^T f_t(M)
\end{align*}
for all $M$, where we use the fact that $M_{T+1}$ is a global minimizer of $\psi(M) + \sum_{t=1}^T f_t(M)$ for 
the last inequality. This completes the induction and hence the proof.
\end{proof}

As a corollary, we have (compare to Proposition~\ref{prop:ftrl-aux}):
\begin{corollary}
\label{cor:ftrl-k-aux}
Suppose that we choose $M_t = \frac{1}{t} \sum_{s=1}^{t-1} Z_s$. Then, assuming 
$\|Z_t\|_{op} \leq 1$ for all $t$, we have
\[ \sum_{t=1}^T (Z_t - M_t)^2 \preceq 2\sum_{t=1}^T (Z_t - M^*)^2 + 6I, \]
for $M^* \eqdef \frac{1}{T} \sum_{t=1}^T Z_t$.
\end{corollary}
\begin{proof}
The key observation is the \emph{matrix Young's inequality}: 
$AB + BA \preceq \frac{1}{\gamma}A^2 + \gamma B^2$ for all symmetric $A$, $B$ and 
all $\gamma > 0$. (This follows immediately upon expanding 
$(A/\sqrt{\gamma} - \sqrt{\gamma} B)^2 \succeq 0$.) We then note that 
$M_t$ obeys Lemma~\ref{lem:ftrl-k} with $\psi(M) = M^2$ and $f_t(M) = (M-Z_t)^2$. 
Hence we have
\begin{dgroup*}
\begin{dmath*} \sum_{t=1}^T (Z_t - M_t)^2 - (Z_t - M^*)^2
\end{dmath*}\begin{dmath*} \preceq (M^*)^2 + \sum_{t=1}^T (Z_t - M_t)^2 - (Z_t - M_{t+1})^2 
\end{dmath*}\begin{dmath*} = (M^*)^2 + \sum_{t=1}^T \left[Z_t(M_{t+1} - M_t) + (M_{t+1}-M_t)Z_t + M_t^2 - M_{t+1}^2 \right]
\end{dmath*}\begin{dmath*} = (M^*)^2 + M_1^2 - M_{T+1}^2 + \sum_{t=1}^T \frac{1}{t+1}\left[ Z_t(Z_t-M_t) + (Z_t-M_t)Z_t\right] 
\end{dmath*}\begin{dmath*} \preceq I + \sum_{t=1}^T \frac{Z_t^2}{\gamma (t+1)^2} + \gamma (Z_t - M_t)^2 
\end{dmath*}\begin{dmath*} \preceq I + \frac{I}{\gamma} + \gamma \sum_{t=1}^T (Z_t - M_t)^2.
\end{dmath*}
\end{dgroup*}
Re-arranging yields
\begin{equation*}
\sum_{t=1}^T (Z_t - M_t)^2 \leq \frac{1}{1-\gamma} \left( \frac{1+\gamma}{\gamma}I + \sum_{t=1}^T (Z_t - M^*)^2\right),
\end{equation*}
which for $\gamma = \frac{1}{2}$ again yields the desired result.
\end{proof}
Combining Proposition~\ref{prop:maeg} with Corollary~\ref{cor:ftrl-k-aux} gives a 
regret bound for the MEG-Variance algorithm, whose updates are given in 
Table~\ref{tab:algorithms}.
\begin{corollary}
\label{cor:maeg-variance}
For $0 < \eta \leq \frac{1}{4}$ and $\|Z_t\|_{op} \leq 1$, the MEG-Variance algorithm achieves a regret bound of
\begin{dmath}\Regret(w) \leq \frac{\log(n)}{\eta} + \eta \left[ \sum_{t=1}^T \Tr(W(Z_t-M^*)^2) + 4\log(T+1) \right].\end{dmath} 
\end{corollary}

### 2014-01-27 lp/paper_icml.tex
done with mw12 draft
done with machinery
done with ftrl-aux
done with matrix section
added algorithms-table
mostly fixed equation formatting
proofread a first draft, now just need to add a conclusion

\documentclass{article}
\usepackage{import, subfiles}
\usepackage{hyperref, icml2014, times}
\usepackage{tabularx}
\input{latex-defs.tex}

@@

\icmlauthor{Jacob Steinhardt}{jsteinhardt@cs.stanford.edu}
\icmladdress{Stanford University,
             353 Serra Street, Stanford, CA 94305 USA}
\icmlauthor{Jonathan Huggins}{jhuggins@mit.edu}
\icmladdress{MIT CSAIL,
             77 Massachusetts Avenue, Cambridge, MA 02139 USA}
\icmlauthor{Percy Liang}{pliang@cs.stanford.edu}
\icmladdress{Stanford University,
             353 Serra Street, Stanford, CA 94305 USA}

@@

\begin{abstract} 
We present an adaptive variant of the exponentiated gradient algorithm, 
achieving regret that depends only on the variance of the best retrospective 
expert. This generalizes and improves a result by 
\cite{hazan2010variation}. Our analysis is conceptually clean and brings together 
two recent developments in online learning, as well as a novel construction 
using an auxiliary instance of follow the regularized leader to tune a regret 
bound. Using the machinery developed, we are also able to extend our results 
to the matrix case, presenting an \emph{adaptive matrix exponentiated gradient} 
algorithm. Our proof in this case involves a novel analysis tool generalizing 
follow the regularized leader to vector-valued payoffs, which may be of 
independent interest.
\end{abstract}

\subfile{introduction.tex}
\subfile{algorithms.tex}

>>>>

\documentclass{article}
\usepackage{import, subfiles}
\usepackage{hyperref, icml2014, times}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}
\input{latex-defs.tex}
\usepackage{breqn}

@@

\icmlauthor{Jacob Steinhardt}{jsteinhardt@cs.stanford.edu}
\icmladdress{Stanford University,
             353 Serra Street, Stanford, CA 94305 USA}
%\icmlauthor{Jonathan Huggins}{jhuggins@mit.edu}
%\icmladdress{MIT CSAIL,
%             77 Massachusetts Avenue, Cambridge, MA 02139 USA}
\icmlauthor{Percy Liang}{pliang@cs.stanford.edu}
\icmladdress{Stanford University,
             353 Serra Street, Stanford, CA 94305 USA}

@@

\begin{abstract} 
We present an adaptive variant of the exponentiated gradient algorithm, 
achieving regret that depends only on the variance of the best retrospective 
expert. This generalizes and improves a result by 
\cite{hazan2010variation}. Our analysis is conceptually clean and brings together 
two recent developments in online learning, as well as a novel construction 
using an auxiliary instance of follow the regularized leader to tune a regret 
bound. Using the machinery developed, we are also able to extend our results 
to the matrix case, presenting an \emph{adaptive matrix exponentiated gradient} 
algorithm. Our proof in this case involves an analysis tool generalizing 
follow the regularized leader to vector-valued payoffs, which may be of 
independent interest.
\end{abstract}

\subfile{introduction.tex}
\subfile{algorithms-table.tex}
\subfile{mw12.tex}
\subfile{machinery.tex}
\subfile{ftrl-aux.tex}
\subfile{matrix.tex}
\subfile{conclusion.tex}
